R Notebook for conducting Minimum Detectable Change (MDC) Analysis to design a monitoring strategy for the Upper Yaquina River TMDL Implementation Plan

### 2024-02-21 msc.Rmd
fixed the y labels of the bar plot of MDCs by station

    theme_minimal() + 
  labs(title='MDC by Station', x='Station', y='% MDC') +
  scale_y_continuous(limits = c(0, 10), 
                     labels = label_number(scale = 1, accuracy = 0.0)) +
  theme(legend.position = "none")

@@

df_cur <- df_log10 %>% filter(STATION == "12301") 
str(df_cur)

@@

print(paste("MDC for", initial_n + additional_samples, "total samples:", 
            sprintf("%f6", MDC_add), " compared to ", sprintf("%f6", MDC_cur),
            " for ", initial_n, " initial samples"))

>>>>

    theme_minimal() + 
  labs(title='MDC by Station', x='Station', y='% MDC') +
  scale_y_continuous(limits = c(0, 10), 
                     labels = label_number(scale = 1, accuracy = 0.1)) +
  theme(legend.position = "none")

@@

df_cur <- df_log10 %>% filter(STATION == "12301")

@@

print(paste("MDC for", initial_n + additional_samples, "total samples:", 
            sprintf("%.2f", abs(10^(MDC_add) - 1) * 100)), "% compared to",
            sprintf("%.2f", abs((1 - 10^(-MDC_cur)) * 100)),
            "% for", initial_n, "initial samples"))
